---
title: "xai2shiny introduction: Titanic dataset with multiple models"
author: Adam Rydelek, Mateusz Polakowski
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette_titanic_rf_glm_h2o}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

```{r}
library("xai2shiny")
```

# Titanic dataset

`DALEX` packages provides an imputed version of a common classification-oriented dataset - `titanic` (data was copied from the `stablelearner` package).
Let's see a sample of observations:

```{r}
library("DALEX")
head(titanic_imputed, 3)
```

# Models to compare

Package allows to pass multiple models from different packages to the main function, so why not create some:

```{r}
library("ranger")

model_rf <- ranger(survived ~ .,
                   data = titanic_imputed,
                   classification = TRUE,
                   probability = TRUE)
model_glm <- glm(survived ~ .,
                 data = titanic_imputed,
                 family = "binomial")
```

# Explainers based on models

In fact, `xai2shiny` function accepts only explainers, i.e. `DALEX` special objects basing on provided models. Let's create all necessary explainers:

```{r results='hide'}
explainer_rf <- explain(model_rf,
                        data = titanic_imputed[,-8],
                        y = titanic_imputed$survived)
explainer_glm <- explain(model_glm,
                         data = titanic_imputed[,-8],
                         y = titanic_imputed$survived)
```

# Shiny application

After that, the only thing left to do is to generate an app and run it:

```{r eval=FALSE}
xai2shiny(explainer_rf, explainer_glm, directory = './', run = TRUE)
```

# Cloud deployment

Further cloud deployment can be done in 2 simple steps (see [README example](https://github.com/ModelOriented/xai2shiny/blob/master/README.md) for details):

```{r eval=FALSE}
xai2shiny::cloud_setup()
my_droplet_id <- 1 # Compare it to your DigitalOcean account and set a proper ID 
deploy_shiny(droplet = my_droplet_id, path = './xai2shiny', packages = "ranger")
```

# External package's model

As `xai2shiny` covers as many external models sources as `DALEX` and `DALEXtra`, let's consider widely known `mlr3` package:

```{r eval=FALSE}
library("DALEXtra")
library("mlr3")
library("mlr3learners")

titanic <- titanic_imputed
titanic[, 'survived'] <- as.factor(titanic[, 'survived'])

task <- TaskClassif$new(id = 'titanic', 
                        backend = titanic, 
                        target = "survived", 
                        positive = '1')

learner <- mlr_learners$get('classif.log_reg')
learner$predict_type = "prob"

train_set = sample(task$nrow, 0.8 * task$nrow)
test_set = setdiff(seq_len(task$nrow), train_set)

learner$train(task, row_ids = train_set)
explainer_mlr <- explain_mlr3(learner,
                              data = titanic[,-8], 
                              y = as.numeric(as.character(titanic$survived)),
                              label = "mlr3 model")
xai2shiny(explainer_mlr, directory = "./", run = FALSE)
```
